Wikipedia WALS Feature Analysis

### 2019-07-17 surprisal/MacWhinney poster/poster_plotting.Rmd
feature space and cosine distances joined

Get utterances
```{r get_utterances}
childes <- read_feather(here("Data/childes_surprisals.feather")) %>%
  clean_names() %>%
  mutate(speaker_role = if_else(speaker_role == "Adult", "Parent", "Child"))

switchboard <- read_feather(here("Data/switchboard_surprisals.feather")) %>%
  clean_names() %>%
  mutate(language = "English", speaker_role = "Adult") %>%
  select(-corpus)
```

@@

pdf("surprisals.pdf", width = 10, height = 5.5)
data %>%
  filter(length == 8) %>%
   ggplot(aes(x = word_order, y = s,
                        color = speaker_role,
                        label = speaker_role)) +
  facet_grid(context ~ language, scales = "free") +
  geom_point(size = 1.5) +
  geom_line(size = 1.5) +
  scale_color_brewer(palette = "Set1") + 
  theme(legend.position = "none") +
  geom_text(data = label_data, size = 6) + 
  labs(x = "Word Position", y = "Average Information")
dev.off()
```

>>>>

Get utterances
```{r get_utterances}
childes <- read_feather(here("Data/childes_words.feather")) %>%
  clean_names() %>%
  mutate(speaker_role = if_else(speaker_role == "Adult", "Parent", "Child"))

switchboard <- read_feather(here("Data/switchboard_words.feather")) %>%
  clean_names() %>%
  mutate(language = "English", speaker_role = "Adult") %>%
  select(-corpus)
```

@@

# pdf("surprisals.pdf", width = 10, height = 5.5)
data %>%
  filter(length == 8, language != "Mandarin") %>%
   ggplot(aes(x = word_order, y = s,
                        color = speaker_role,
                        label = speaker_role)) +
  facet_grid(language~context, scales = "free") +
  geom_point(size = 1.5) +
  geom_line(size = 1.5) +
  scale_color_brewer(palette = "Set1") + 
  theme(legend.position = "none") +
  geom_text(data = label_data, size = 6) + 
  labs(x = "Word Position", y = "Average Information")
# dev.off()
```

### 2019-07-17 surprisal/WALS_features.Rmd
feature space and cosine distances joined

```{r setup, include=FALSE}
library(tidyverse)
library(lingtypology)
library(feather)
library(here)
library(missMDA)
library(lsa)
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(lingtypology)
library(feather)
library(here)
library(missMDA)
library(lsa)
library(reshape2)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r feature space}
imputed_df <- read_csv(here("Data/imputed_wals.csv"))

feature_space <- imputed_df %>% 
  gather(feature, value, -language) %>% 
  group_by(feature) %>% 
  mutate(value = as.numeric(as.factor(value))) %>% 
  spread(feature, value) %>%
  column_to_rownames("language") %>%
  dist(method = "manhattan") %>%
  as.matrix() %>%
  melt(value.name = "distance") %>%
  as_tibble() %>%
  rename(language1 = Var1, language2 = Var2)

feature_space %>%
  count(distance) %>%
  mutate(n = n/2) %>% 
  ggplot(aes(x = distance, y = n)) + 
    geom_col() + 
    scale_y_continuous(breaks = 1:12)
```

```{r cosines}
cosines <- wiki %>%
  filter(language %in% common_languages, gram == "Unigram") %>%
  select(-gram) %>% 
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, cosine, -language1) %>%
  mutate(cosine = 1 - abs(cosine))

all_distances <- cosines %>%
  left_join(feature_space)
```
